%!TEX root = _all.tex

Alternatively, the energy savings that we have been able to identify for both the heating and the cooling are also of different orders of magnitude. 

It's also important to point out that the latent component of the heating and the cooling scenarios are fundamentally different. For the heating scenario, the latent load is the humidity that needs to be added by humidifiers to maintain satisfying level of humidity (50\% in this study). For the cooling scenario, the latent load we were comparing was obtained by separating the sensible from the total cooling demand resulting from outdoor air. Therefore, for the heating scenario, the energy that needs to be added to the air through humidifiers cannot be directly translated into energy demand. For the cooling scenario, the the differences between the latent energy are in fact the energy demands that can be reduced through selection of different set points.

However, regarding the humidity removal process,it's also important to point out that neither of the scenarios can be directly translated into energy savings as there may potentially be different systems invovled in achieving the desirable state of humid air. This allowed us to avoid focusing on a specific type of building system and its corresponding component effiiencies within the scope of this analysis. Further discussions regarding the benefits of selecting certain humidity removal technologies, such as the chilled water cooling/heating system, dual (dessicant and enthalpy) wheel or direct exchange cooling coils.
