\documentclass[review]{elsarticle}
\usepackage{lineno,hyperref,amsmath,adjustbox,todonotes,gensymb,float,afterpage}
\usepackage[margin=0.95in]{geometry}
\usepackage{setspace}
\usepackage[T1]{fontenc}
\bibliographystyle{elsarticle-num}
\journal{Applied Energy}
\begin{document}\begin{frontmatter}
\title{Psychrometrically characterizing the humidity and energy benefits of widening indoor set point temperatures}
\author[mysecondaryaddress]{Hongshan Guo\corref{mycorrespondingauthor}}
\author[mymainaddress,mysecondaryaddress]{Forrest Meggers}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{fmeggers@princeton.edu}
\address[mymainaddress]{School of Architecture, Princeton University, USA}
\address[mysecondaryaddress]{Andlinger Center for Energy and the Environment, Princeton University, USA.}
\begin{abstract}
Among other approaches of reducing building-related energy usage, modifying the indoor air temperature set points has been proven a very efffective approach. Building on recent findings that expanding the range of set points can achieve the same level of occupant comfort while achieving energy savings, we want to investigate the possibilities of pushing the set point ranges further in this study. To achieve the further expanded indoor air temperature set point yet still addressing the heating/cooling loads, we assumed the usage of supplemental radiant heating and cooling systems in average household across the continental US. Interpolating the psychrometric processes across the weather data we collected, we were able to show the importance of having humidifiers for all-air systems through a spatial analysis. Our analysis also showed that more than 60\% of the dehumidification energy demand can be mitigated from a higher set point during the cooling season. These results are helpful to illustrate the inherent strength of radiant systems when addressing latent demands in the indoor environments. Further investigations on how different occupancy schedule and occupant density may be helpful in advancing our understanding on the latent-load-mitigation capability of radiant systems.
\end{abstract}
\begin{keyword}relative humidity\sep radiant heating and cooling\sep cooling degree days\sep latent loads\end{keyword}\end{frontmatter}
\tableofcontents
\section{Introduction}
\input{1intro.tex}
\section{Methodology}
    % \subsection{Base Assumptions}
    %     \input{2_1Exi_indoor.tex}    
    \subsection{Cooling, Heating and Enthalpy Degree Days}
        \input{2_2Exi_outdoor.tex}
    \subsection{Data Collection and Processing}
        \input{2_3DataCollection}
\section{Results}
    \subsection{Heating scenario and resulting RHs}
    \input{3_1simp_occup.tex}
    \subsection{Cooling scenario and resulting Energy Savings}
    \input{3_2simp_envi.tex}
\section{Discussions and Conclusions}
    \subsection{Relative Humidity improvements}
    \input{4_2_Subjective.tex}
    \subsection{Extra energy savings and demands}
    \input{4_1_Objective.tex}
\section{Conclusion}
\input{5_conclusions.tex}
\bibliography{top.bib}
\end{document}